Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/type-theory.tex

To reconstruct proofs generated by \Metis, we have formalized in type theory the classical propositional logic.
A  briefly description of it is presented in Appendix~\ref{app:CPL}. In this
formalization, we assume the principle of excluded third (\abbre{PEM}) as the
only axiom since \Metis is a prover for classical logic. Assuming \abbre{PEM},
we can justify refutation proofs by deriving from it the \emph{reductio ad
absurdum} rule (\abbre{RAA}). The \abbrev{RAA} rule is the formulation of the
principle of proof by contradiction, that is, a derivation of a contradiction,
$⊥$, from the hypothesis $(¬ φ)$, is a derivation of $φ$.

\begin{notation}
We write theorems in \CPL as the family of dependent types, $Γ ⊢ φ$ where
the turnstile symbol (⊢) represents the syntactical consequence relation
between a set of premises, $Γ : \List~\Prop$ and a conclusion $φ : \Prop$.
$\abbre{List}$ type is the usual inductive type for lists.
\end{notation}

>>>>

To reconstruct proofs generated by \Metis, we have formalized in type
theory the classical propositional logic.  A briefly description of it
is presented in Appendix~\ref{app:CPL}. In this formalization, we
assume the principle of excluded third (henceforth \abbre{PEM}) as the
only axiom since \Metis is a prover for classical logic. Assuming
\abbre{PEM}, we can justify refutation proofs by deriving from it the
\emph{reductio ad absurdum} rule (henceforth \abbre{RAA}). The
\abbrev{RAA} rule is the formulation of the principle of proof by
contradiction, that is, a derivation of a contradiction,~$⊥$, from the
hypothesis~$¬ φ$, is a derivation of~$φ$.

\begin{notation}
  The $\abbre{List}$ type is the usual inductive and parametric type
  for lists. We formalise theorems in \CPL by an inductive family
  $\_⊢\_$ indexed by a list of propositions and a proposition, that
  is, $Γ ⊢ φ$ represents the syntactical consequence relation between
  a list of premises, $Γ : \List~\Prop$ and a conclusion $φ : \Prop$.
\end{notation}
